\documentclass[conference,10pt,letter]{IEEEtran}

\usepackage{url}
\usepackage{amssymb,amsthm}
\usepackage{graphicx,color}

%\usepackage{balance}

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color, colortbl}
\usepackage{times}
\usepackage{caption}
\usepackage{rotating}
\usepackage{subcaption}

\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}

\newcommand{\XXXnote}[1]{{\bf\color{red} XXX: #1}}
\newcommand{\YYYnote}[1]{{\bf\color{red} YYY: #1}}
\newcommand*{\etal}{{\it et al.}}

\newcommand{\eat}[1]{}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\im}{\item}
\newcommand{\eg}{{\it e.g.}\xspace}
\newcommand{\ie}{{\it i.e.}\xspace}
\newcommand{\etc}{{\it etc.}\xspace}

\def\P{\mathop{\mathsf{P}}}
\def\E{\mathop{\mathsf{E}}}

\begin{document}
\sloppy
\title{Detecting truck driver's fatigue and distractions using Convolutoinal Neural Networks}
\maketitle
\begin{abstract}

    Driving a truck when the driver is experiencing fatigue and distractions 
    is considered unsafe. Therefore, controlling the driver's in-cabin behavior is 
    an important task (for example at mines and on roads). Once the event is detected 
    the system can send a sound alert to the truck driver and notify site operations 
    that unsafe driving behavior was detected.

    In this document, we describe a prototype implementation of a simple solution that 
    detects fatigue and distractions events and notifies the control center. Our solution 
    is based on convolutional neural networks (CNN) combined with a regular neural network 
    to detect distractions and fatigue instances. Apart from the image recognition we also 
    wrote a simple backend that is capable of collecting GPS coordinates, short video 
    clips, and actual events in the database (fatigue and distraction). The user interface 
    allows the controller to confirm and, if necessary, correct the events for further 
    updating the CNN model. All events are displayed on the map for analysis. Historical 
    data browsing is also possible for more in-depth analysis of the driver's behavior. 
    
    We have trained the neural network with $500$ labeled images (we had three categories or classes in our dataset: 
    distraction, fatigue, and regular, normal operation), and verified the accuracy of the solution using another 
    $500$ images (unlabeled). The validation was performed by visually inspecting $500$ images and comparing them to 
    the predicted result. The CNN, apart from classification, was also outputing a bounding box.  


\end{abstract}
\input intro.tex
%\input background.tex
%\input hardware.tex
%\input experimental.tex
%\input conclusions.tex
%\balance
%\bibliographystyle{abbrv}
%\bibliography{mybib}

\end{document}

